Freezing of a Weeks-Chandler-Anderson Fluid using classical Density Functional Theory

### 2020-10-15 papers/thesis-kirstie/thesis.tex
more edits

In the late 1950s, Scaled Particle Theory (SPT) was developed~\cite{Reiss Frich Lebowitz} from which an equation of state, and
an expression for the excess Helmholtz free energy of a homogeneous Hard-Sphere fluid can be obtained~\cite{Hansen}. 
%Percus and Yevick took another approach to the Hard-Sphere fluid.
In 1961 Morita and Hiroike introduced a density functional approach to finding an expression for the 
excess Helmholtz free energy of inhomogeneous fluids~\cite{MoritaDFT}.
% ?  Percus-Yevick applied Density Functional Theory (DFT) to find an expression for the excess 
Helmholtz free energy of an inhomogeneous Hard-Sphere fluid. 
In 1967 %the late 1960s, and early 1970s, 
Barker and Henderson~\cite{barker1967perturbation} adapted perturbation methods to use with fluids composed of 
spheres with softly fading potential functions rather than the hard edges of the spheres 
in the Hard-Sphere fluid. This was done by making the radius of the spheres temperature dependent, 
so that at low temperatures the Soft-Sphere fluid could be modeled by hard spheres with large radii, 
and at high temperatures the Soft-Sphere fluid could be modeled by hard spheres with smaller radii. 
%A larger radii cooresponds to a deeper level of penetration of two soft spheres into each other when they collide at higher temperatures.
%The different size radii coorespond to the different depths to which two soft spheres would penetrate into each other when they collide. 
This reflects the idea that soft-spheres penetrate more deeply into each other when they collide at higher temperatures. 
Weeks, Chandler, and Anderson studied the soft repulsive portion of the Leonard-Jones potential~\cite{andersen1971relationship}, 
which became known as the Weeks-Chandler-Anderson model fluid.

>>>>

In the late 1950s, Scaled Particle Theory (SPT) was developed~\cite{ReissSPT} from which an equation of state, and
an expression for the excess Helmholtz free energy of a homogeneous Hard-Sphere fluid can be obtained~\cite{Hansen}. 
%Percus and Yevick took another approach to the Hard-Sphere fluid.
In 1961 Morita and Hiroike introduced a density functional approach to finding an expression for the 
excess Helmholtz free energy of inhomogeneous fluids~\cite{MoritaDFT}.
% ?  Percus-Yevick applied Density Functional Theory (DFT) to find an expression for the excess 
Helmholtz free energy of an inhomogeneous Hard-Sphere fluid. 
In 1967 %the late 1960s, and early 1970s, 
Barker and Henderson~\cite{barker1967perturbation} adapted perturbation methods to use with fluids composed of 
spheres with softly fading potential functions rather than the hard edges of the spheres 
in the Hard-Sphere fluid. This was done by making the radius of the spheres temperature dependent, 
so that at low temperatures the Soft-Sphere fluid could be modeled by hard spheres with large radii, 
and at high temperatures the Soft-Sphere fluid could be modeled by hard spheres with smaller radii. 
%A larger radii cooresponds to a deeper level of penetration of two soft spheres into each other when they collide at higher temperatures.
%The different size radii coorespond to the different depths to which two soft spheres would penetrate into each other when they collide. 
This reflects the idea that soft-spheres penetrate more deeply into each other when they collide at higher temperatures. 
Weeks, Chandler, and Anderson studied the soft repulsive portion of the Leonard-Jones potential~\cite{andersen1971relationship}, 
which became known as the Weeks-Chandler-Anderson model fluid.
